Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-05 main_paper.tex
Minor notational fix in appendix
Revise normality proof for wild bootstrap
Basically asserts that Liapunov's condition holds.

Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
implies that
\begin{align*}
  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
    \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
\end{align*}
with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
These coefficients are related to the quantities of interest by
\begin{equation*}
  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
\end{equation*}
for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
\begin{equation*}
  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
\end{equation*}

@@

To prove convergence in probability of the bootstrap variance, note that the
wild bootstrap ensures that, for any function $z(\cdot)$,
\begin{equation*}
  \V^*\Big(\sum_{i=1}^n z(X_i) \varepsilon_i^*\Big)
  = \sum_{i=1}^n z(X_i)^2 \hat\varepsilon_i^2.
\end{equation*}
So, given this expression for the iterated bootstrap and the formula for the
variance conditional on $X$ presented at the end of the introduction to this
appendix, it suffices to show that
\begin{gather}
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
  \label{eq:3} \\
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{m'} \Psit_{\bullet,1,2}(h,b)
  + o_p(\tfrac{1}{m'})
  \label{eq:5} \\
  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
  \label{eq:7}
\end{gather}
But these convergence results follow from CCT's results on
$\hat\mu_{\bullet,p}^{(\nu)}$, Lemma SA3 in particular.

By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
  &V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}) \\
  &\leq \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times
    \tr(V'(h,b)^{-1/2} \Omega_\bullet(h,b)' \Omega_\bullet(h,b)V'(h,b)^{-1/2}) \\
  &= \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \to^{p^{*}} 0$. Let
$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
realized values of $\epb_\bullet$ with replacement and let
$\bar{\varepsilon}^\circ = (1/M_\bullet(b)) \osum[\bullet]{i}{b} \varepsilon^\circ_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{\bullet,1}^*, \varepsilon_{\bullet,1})
  \leq
  \Big((\bar\varepsilon^{\circ})^2 +
  (2/M_\bullet(b)) \osum[\bullet]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
  + \rho(\varepsilon^\circ_1,\ \varepsilon_{\bullet,1}).
\end{equation*}
But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
\[
  (1/M_\bullet(b)) \osum[\bullet]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\varepsilon_1^\circ,\ \varepsilon_{\bullet,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed

>>>>

Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
implies that
\begin{align*}
  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
  \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
\end{align*}
with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
These coefficients are related to the quantities of interest by
\begin{equation*}
  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
\end{equation*}
for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
\begin{equation*}
  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
\end{equation*}

@@

To prove convergence in probability of the bootstrap variance, note that the
wild bootstrap ensures
\begin{equation*}
  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
\end{equation*}
for any measurable function $R(\cdot)$.
Given this expression for the iterated bootstrap and the formula for the
variance conditional on $X$ presented at the end of the introduction to this
appendix, it suffices to show that
\begin{gather}
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
  \label{eq:3} \\
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
  + o_p(\tfrac{1}{b^2})
  \label{eq:5} \\
  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
  \label{eq:7}
\end{gather}
But these convergence results follow from CCT's results on
$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
and standard arguments on the convergence of residuals to
the population error term.

Normality also follows standard arguments for the Wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$p$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
\rvert^{p}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1'$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish~\eqref{eq:17}
and complete the proof. \qed
